\cvsection{Experience}
\begin{cventries}
    \cventry
        {Technical Cofounder}
        {Marcillac}
        {Remote}
        {2021 - Present}
        {
            \begin{cvitems}
                \item{Formal Software Verification (Under NDA)}
            \end{cvitems}
        }
    \cventry
        {Neural Architect, Computational Geometer}
        {The Bracket Studio}
        {Remote}
        {2021 - Present}
        {
            \begin{cvparagraph}
A Neural Architect or Neural Designer is a constructor of neuroscience informed neural networks that are embedded in a geometric space. Traditionally, neural networks are embedded in a Hilbert space, or you might say they aren't embedded at all, as anything can be adjacent to anything and everything. Constraining network designs to those that could actually exist in 2D or 3D space (when constructed with non-zero size components) aids interpretability without hampering expressivity.
            \end{cvparagraph}
        }
    \cventry
        {Software Engineer}
        {Dolthub}
        {Dallas, TX}
        {2020 - Present}
        {
            \begin{cvparagraph}
                Dolt adds revision control capabilities and git semantics to SQL databases. I preside over data bounties, contests in which our community members collaborate and compete to construct large and intriguing datasets.
            \end{cvparagraph}
            \begin{cvitems}
                \item{Interfaced with our Discord community, answering bounty participant questions and reviewing their pull requests.}
                \item{Designed the data bounties, from the contest copy to the sql schemas, and prototyped the collection process to anticipate participant difficulties.}
                \item{Wrote programs to facilitate working with and understanding massive datasets.}
            \end{cvitems}
        }
    \cventry
        {Freelance Tutor}
        {OfficeHours.com, Upwork, Chegg}
        {Dallas, TX}
        {2018 - Present}
        {
            \begin{cvparagraph}
                Tutoring is diagnostic in nature; often there is one small misunderstanding that once uncovered and corrected allows everything to fall in place. I find being the catalyst aiding in such transformations to be deeply rewarding. I enjoy the dual challenge of comprehending both the subject matter and the student in order to make the complex accessible. Subjects tutored listed in "Certifications" section.
            \end{cvparagraph}
        }
    \cventry
        {Bioinformatician}
        {Self-Decode}
        {Dallas, TX}
        {2019 - 2020}
        {
            \begin{cvparagraph}
            I worked as a bioinformatician (bioinformaticist) for Self-Decode, which involved understanding and transforming primary literature in medicine, statistics, and computer science. 
            \end{cvparagraph}
            \begin{cvitems}
                \item{Worked with massive genomic files.}
                \item{Calculated polygenic and behavioral risk scores for serious illnesses, such as cancers, heart disease, and COPD.}
                \item{Designed procedures to convert these scores to "intuitive, human useful" measures.}
                \item{Worked on a risk assessment for COVID-19, which estimated the severity of a case of coronavirus, given background risk factors such as age and pre-existing conditions.}
            \end{cvitems}
        }
    \cventry
        {Software Engineer, Virtual Assistants and Home Automation}
        {Google}
        {Mountain View, CA}
        {2014 - 2015}
        {
        \begin{cvparagraph}
            As a member of the Third Party Actions team, I enabled interactions between third-party developers and Google Assistants.
         \end{cvparagraph}
	    \begin{cvitems}
            \item{Handled the integration of Nest Smart Thermostats with Google services.}
            \item{Engaged in grammar engineering to bind search queries to the appropriate response.}
            \item{Attended TGIFs, weekly all-hands meetings on the global mission and activities of Google.}
            \item{Learned and used internal and open-source tools for maintaining and modifying the largest codebase in human history.}
        \end{cvitems}
        }
    \cventry
        {Undergraduate TA}
        {Duke University Computer Science Department}
        {Durham, NC}
        {2011 - 2013}
        {
            \begin{cvitems}
                \item{Served as a TA for Computer Design/Organization and Introduction to Operating Systems.}
                \item{Conducted review sessions, held office hours, and helped students via Piazza (a classroom Q\&A service).}
                \item{Met with professors to discuss student progress and to help plan the course.}
                \item{Graded assignments and projects.}
            \end{cvitems}
        }
    \cventry
        {Premedical Student}
        {Medical Shadowing}
        {Dallas, TX}
        {2010 - 2013}
        {
            \begin{cvitems}
                \item{Duke Neurosurgery (Durham, NC)}
                \item{Methodist Hospital - Cardiology, Gastroenterology, Surgery}
                \item{Lewisville Medical Center - Oncology, Radiology}
            \end{cvitems}
        }
    \cventry
        {Journalist}
        {Citizen's Advocate}
        {Coppell, TX}
        {2007 - 2009}
\end{cventries}
